Comparative effectiveness of BNT162b2 versus Moderna booster doses in England: protocol

### 2022-11-09 protocol/protocol.Rmd
28 day exclusion period, not 90

* they are registered at a GP practice using TPP's SystmOne clinical information system at the time of boosting;
* they received a two-dose primary vaccination course of either BNT162b2 or ChAdOx1-S (mixed dosing and Moderna mRNA-1273 were not considered due to small numbers);
* they are not a health or social care worker, not resident in a care or nursing home; not medically housebound or receiving end-of-life care;
* there is no evidence of SARS-CoV-2 infection or COVID-19 disease within the 90 days prior to booster dose;
* they are not undergoing an unplanned hospital admission at the time of boosting;
* they have complete information on sex, ethnicity, deprivation, and NHS region.

>>>>

* they are registered at a GP practice using TPP's SystmOne clinical information system at the time of boosting;
* they received a two-dose primary vaccination course of either BNT162b2 or ChAdOx1-S (mixed dosing and Moderna mRNA-1273 were not considered due to small numbers);
* they are not a health or social care worker, not resident in a care or nursing home; not medically housebound or receiving end-of-life care;
* there is no evidence of SARS-CoV-2 infection or COVID-19 disease within the 28 days prior to booster dose;
* they are not undergoing an unplanned hospital admission at the time of boosting;
* they have complete information on sex, ethnicity, deprivation, and NHS region.
